%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shahriar}{Velayat}{Full Stack Software Engineer}
{\contactlines
{\href{https://www.github.com/ShahriarVelayat}{ShahriarVelayat}}
{\href{https://www.linkedin.com/in/shahriar-velayat/}{shahriar-velayat}}
{\href{shahriarvelayat@gmail.com}{shahriarvelayat@gmail.com}}
{\href{tel:+shahriarvelayat@gmail.com}{+989333285099}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objective}

I am an accomplished software engineer with a strong background in web application development. Skilled in various aspects of software engineering, I have a demonstrated history of delivering high-quality solutions. With a focus on web application development, I am committed to driving innovation and excellence in software development.

\section{Experience}

\runsubsection{{\href{https://policytek.com/}{Policytek.com}}}
\descript{| Senior Backend Developer }
\location{April 2023 – present | Remote , San Diego , U.S.}
\vspace{\topsep}
\begin{tightemize}
\sectionsep
\item Developing a CRM system to efficiently manage policies and customer leads.
\item PolicyTek is a CRM used to manage leads from the initial call to selling life insurance to customers.
\item  Tools \& Technologies : NestJs,MongoDB,Angular,Ionic,Websocket,Docker
\end{tightemize}
\sectionsep

\runsubsection{{\href{https://www.netware.studio/}{Netware Studio}}}
\descript{| Senior Backend Developer}
\location{June 2021 – Current | Tehran, Iran}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item Developing an app to assist customers in managing their health and fitness. \href{https://sira.fit} Sira.fit 
\item Developing a IoT framework to manage industrial and home use gadgets.  \href{https://www.ovio.ir}{Ovio.ir} 
\item Developing a flight booking system   \href{https://mysafar.com}{Mysafar.com} 
\item  Tools \& Technologies : NestJs,MongoDB,Angular,Ionic,Websocket,Docker
\end{tightemize}
\sectionsep


\runsubsection{Palapal Pardaz Fars | Appsaz.ir}
\descript{| Full Stack Developer }
\location{Sep 2018 – March 2021 | Shiraz, Iran  }
\begin{tightemize}
\sectionsep
\item Developing custom mobile applications for businesses, handling both the front-end and back-end aspects.
\item Develope and Build Android & IOS Applications
\item Design and Develop REST API
\item  Tools \& Technologies :
     Ionic Framework,MySql,Angular,Wordpress,Php,Redmine Project Manager,Android Studio
\end{tightemize}
\sectionsep

\runsubsection{Aruniq |}
\descript{| Augmented reality Researcher }
\location{Apr 2017 – Feb 2018 | Shiraz, Iran  }
\begin{tightemize}
\sectionsep
\item Specializing in researching and developing Augmented Reality applications for both web and mobile platforms.
\item Developing a mobile application for the Fars Consumer Rights Support Organization, leveraging Marker-Less Augmented Reality technology.
\item  Tools \& Technologies : Apache Cordova - Android - ARToolkit - Unity
\end{tightemize}
\sectionsep


\runsubsection{EvoTeam |}
\descript{| Android Developer}
\location{Oct 2016 – May 2017 | Shiraz, Iran  }
\begin{tightemize}
\sectionsep
\item Developing a Mobile Application for Shiraz University to collect traffic data.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{XCollision}
\descript{| Mobile game}
\location{2018 - 2021}
\begin{tightemize}
\item Designing and developing APIs specifically tailored for managing mobile games
\item  Tools \& Technologies :MySql,Wordpress,Php,Redmine Project Manager
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2020	     & Finalist & Lorem Ipsum\\
% 2018	     & $2^{nd}$ & Dolor Sit Amet\\
% 2015	     & Finalist  & Cras posuere\\
% \\
% \end{tabular}
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\sectionsep
\location{Proficient:}
 TypeScript \textbullet{} JavaScript  
  \textbullet{} MongoDb  
\sectionsep
\location
\location{Experienced:}
Java   \\
\sectionsep
\location{Familiar:}
 Python \textbullet{}  Shell  \\
\sectionsep
\sectionsep
\subsection{Libraries/Frameworks}
\sectionsep
Ionic Framework \textbullet{} Node.js \textbullet{} NestJs \textbullet{} ExpressJs \textbullet{} Angular \textbullet{} Android Development \\
\sectionsep
\sectionsep
\subsection{Tools/Platforms}
\sectionsep
Git \textbullet{} Gitlab \textbullet{} GitLab\-CI/CD     \\ Wordpress \textbullet{} Docker \textbullet{} Linux  \textbullet{} Kubernetes    \textbullet{} Ansible

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Shiraz University of Technology}
\descript{Master's  Degree  Information Technology }
\location{2018 - 2022 }

\sectionsep
\subsection{Shiraz University of Technology}
\descript{Bachelor of Information Technology }{Shiraz University of Technology }
\location{2014 - 2018 }
\sectionsep
\
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     REFERENCES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\location{Engaged with the Shiraz Developers Community.}
\section{}
\sectionsep
\location{Leading introductory Android training courses as an instructor.}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}

% \subsection{Graduate}
% Graduate Algorithms \textbullet{}\\ 
% Advanced Computer Architecture \textbullet{}\\ 
% Operating Systems \textbullet{}\\ 
% Artificial Intelligence \textbullet{}\\
% Visualization For Scientific Data \\
% \sectionsep

% \subsection{Undergraduate}

% Database Management Systems \textbullet{}\\
% Object Oriented Analysis and Design \textbullet{}\\
% Artificial Intelligence and Expert Systems \textbullet{}\\
% Scripting Languages and Web Tech \textbullet{}\\
% Software Engineering \\

\end{minipage} 


\begin{minipage}[t]{0.70\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certification}

\runsubsection{DevOps Engineering Bootcamp}
{{\href{https://rahnemacollege.com/}{Rahnema College}}}
\location{Feb 2022 | Tehran, Iran}
\vspace{\topsep}
\begin{tightemize}
\sectionsep
\item ID : shahriarvelayatLVEh2HqG
\end{tightemize}

\sectionsep
\runsubsection{Java Development}
{South industrial management institute}
\location{Apr 2016 | Tehran, Iran}
\vspace{\topsep}
\begin{tightemize}
\item ID :  2721-9276-1651-1236
\end{tightemize}
\sectionsep

\sectionsep
\runsubsection{Android Development}
{South industrial management institute}
\location{Apr 2016 | Tehran, Iran}
\vspace{\topsep}
\begin{tightemize}
\item ID :  2721-9276-1651-1236
\end{tightemize}
\sectionsep


\sectionsep
\runsubsection{LPIC 1}
{Shiraz University of technology}
\location{Apr 2014 | Shiraz, Iran}
\vspace{\topsep}
\begin{tightemize}
\item ID :  10940
\end{tightemize}
\sectionsep


\sectionsep
\runsubsection{Certified Cisco Network Associate ICND1+ICND2}
{Kahkeshan  Nour}
\location{Apr 2015 | Tehran, Iran}
\vspace{\topsep}
\begin{tightemize}
\item ID :  KN15-CS142233
\end{tightemize}
\sectionsep

\sectionsep
\runsubsection{Network+}
{Kahkeshan  Nour}
\location{Apr 2015 | Tehran, Iran}
\vspace{\topsep}
\begin{tightemize}
\item ID :  KN15-CA542235
\end{tightemize}
\sectionsep

\end{minipage} 

\end{document}  



